---
title: "Short guide to bcc features"
author: "Daniel Lucas Cerqueira"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Short guide to bcc features}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(bcc)
```

# Introduction

`qcc` is a package for **statistical process control and control charts** built based on the `qcc` package, with new functions allowing the use of beta control charts.

This package allows the user to:

- build beta control charts

As the package uses the `qcc` package as the basis for building the graphics, all `qcc` functions and utilities also work on `bcc`. For more informations please consider visiting https://luca-scr.github.io/qcc/.

#Application

You can use `bcc` in two basic ways:

- discrete data representing the sample size using `type = 1`;

- continuous data without sample size with values in the range between [0.1] using `type = 2`; you can make a ratio between the data to be analyzed for example.


#Beta Charts

## Beta Chart for discrete data

```{r}
data("Montgomery2005")
bcc(data=Montgomery2005$Defective, sizes = Montgomery2005$Sample, type=1)
```

##Beta chart for continuos data

```{r}
data("Drapper1998data")
bcc(data = Drapper1998data, type = "2")
```

# References

Montgomery, D.C. (2009) *Introduction to Statistical Quality Control*, 6th ed. New York: John Wiley & Sons.

Scrucca, L. (2004) [qcc: an R package for quality control charting and
statistical process control](http://www.stat.unipg.it/luca/misc/Rnews_2004-1-pag11-17.pdf). *R News* 4/1, 11-17.

SANT'ANNA, Ângelo M. O; CATEN, Carla Schwengber ten. *Beta control charts forsave monitoring fraction data.* Expert Systems With Applications, p. 10236-10243. 1 set. 2012.

----

